Luminosity function and flux function\\ or\\ How far to the brightest beacon?

### 2015-12-08 luminosity.tex
minor phrasing changes; more function () -> []; <> -> \langle \rangle

The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P(F)dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
%%%
\begin{equation}
P(F) dF = C' F^{\alpha } r^{4-2\alpha }
\end{equation}
%%%
where
%%%
\begin{equation}
C' = n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1}
\end{equation}
%%%

The probability to find the maximum flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$, $\mathcal{P} (F_{\rm max}) dF_{\rm max}$ is the joint probability where one of the targets has flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$ and all others have smaller flux. 
The probability to find one object with flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, such a probability is:
%%%
\begin{equation}
\mathcal{P} (F_{\rm max}) dF_{\rm max} = n_r P (< F_{\rm max})^{n_r-1}  P(F_{\rm max}) dF_{\rm max} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%

The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $<F_{\rm max}>$, is obtained by calculating the flowing integral. 
%%%
\begin{eqnarray}
<F_{\rm max}> &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} (F_{\rm max}) \\
&=& n_r \int dF_{\rm max} F_{\rm max} P (< F_{\rm max})^{n_r-1}  P(F_{\rm max})
\end{eqnarray}
%%%

Figure \ref{fig:expectedFmax} shows $<F_{\rm max}>$ as a function of distance $r$ with varying number density of the targets. 
Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 
It is seen that the expected values monotonically decrease as we observe further. This indicates the brightest object is the closest one. \memoYF{??}

@@

%%%
\begin{eqnarray}
&&<F> = \int F \frac{dn}{dF} dF \\
%
&&= \frac{4 \pi C}{5 - 2 \alpha } \\
&& \times \left( \int _{F_{\rm l}} ^{F_{u}} F^{1-\alpha } \left\{ R^{5-2\alpha } - \left( \frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right. dF \\
&&+ \left. \int _{F_{u}} ^{\infty } F^{1-\alpha } \left\{ \left( \frac{L_{\rm max}}{F} \right)^{2.5-\alpha} - \left(\frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right) dF \\
%
&&= \frac{4 \pi C}{5 - 2 \alpha } \\
&& \times \left\{ \left( \frac{F^{2-\alpha } R^{5-2\alpha }}{2-\alpha } - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right. \\
&&\left. + \left( \frac{F^{-0.5}L_{\rm max}^{2.5-\alpha} }{-0.5} - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right\} \\
&&\propto R 
%
\end{eqnarray}
%%%

@@

Probability for a star to have luminosity larger than $L$ is 
%%%
\begin{equation}
P(>L) = \int _L^{\infty} C L^{-\alpha } dL = C \frac{L^{-\alpha +1}}{-\alpha + 1}
\end{equation}
%%%

Probability for a star to have luminosity less than $L$ is 
%%%
\begin{equation}
P(<L) = 1 -P (>L) \end{equation}
%%%

The probability to have the maximum luminosity of $L \sim L + dL$, $\mathcal{P(L_{\rm max}})$, with $N$ samples is
% $expected value of the maximum luminosity $L_{\rm max}$ is
%%%
\begin{eqnarray}
\mathcal{P}(L_{\rm max}) &\cdot & dL_{\rm max} \\
&=& N \cdot p (L_{\rm max}) \cdot P^{N-1}(<L_{\rm max}) \cdot dL_{\rm max} \\
&=& N C L_{\rm max}^{-\alpha } \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1}
\end{eqnarray}
%%%
Thus, the expected value for the maximum luminosity is
%%%
\begin{eqnarray}
< L_{\rm max} > (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
&=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1} \\
&\equiv & N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max})
\end{eqnarray}
%%%

>>>>

The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
%%%
\begin{equation}
P[F] dF = C' F^{\alpha } r^{4-2\alpha }
\end{equation}
%%%
where
%%%
\begin{equation}
C' = n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1}
\end{equation}
%%%

The probability that the maximum flux lies in the range between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$, denoted $\mathcal{P} [F_{\rm max}] dF_{\rm max}$, is the joint probability that one of the targets has flux between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$ and that all others have smaller flux.
The probability that one object has flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, such a probability is:
%%%
\begin{equation}
\mathcal{P} [F_{\rm max}] dF_{\rm max} = n_r P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}] dF_{\rm max} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%

The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm max} \rangle$, is obtained by calculating the flowing integral. 
%%%
\begin{eqnarray}
\langle F_{\rm max} \rangle &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} [F_{\rm max}] \\
&=& n_r \int dF_{\rm max} F_{\rm max} P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}]
\end{eqnarray}
%%%

Figure \ref{fig:expectedFmax} shows $\langle F_{\rm max} \rangle$ as a function of distance $r$ with varying number density of the targets. 
Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 
It is seen that the expected values monotonically decrease as we observe further. This indicates the brightest object is the closest one. \memoYF{??}

@@

%%%
\begin{eqnarray}
&&\langle F \rangle = \int F \frac{dn}{dF} dF \\
%
&&= \frac{4 \pi C}{5 - 2 \alpha } \\
&& \times \left( \int _{F_{\rm l}} ^{F_{u}} F^{1-\alpha } \left\{ R^{5-2\alpha } - \left( \frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right. dF \\
&&+ \left. \int _{F_{u}} ^{\infty } F^{1-\alpha } \left\{ \left( \frac{L_{\rm max}}{F} \right)^{2.5-\alpha} - \left(\frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right) dF \\
%
&&= \frac{4 \pi C}{5 - 2 \alpha } \\
&& \times \left\{ \left( \frac{F^{2-\alpha } R^{5-2\alpha }}{2-\alpha } - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right. \\
&&\left. + \left( \frac{F^{-0.5}L_{\rm max}^{2.5-\alpha} }{-0.5} - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right\} \\
&&\propto R 
%
\end{eqnarray}
%%%

@@

Probability for a star to have luminosity larger than $L$ is 
%%%
\begin{equation}
P[>L] = \int _L^{\infty} C L^{-\alpha } dL = C \frac{L^{-\alpha +1}}{-\alpha + 1}
\end{equation}
%%%

Probability for a star to have luminosity less than $L$ is 
%%%
\begin{equation}
P[<L] = 1 -P [>L] \end{equation}
%%%

The probability to have the maximum luminosity of $L \sim L + dL$, $\mathcal{P(L_{\rm max}})$, with $N$ samples is
% $expected value of the maximum luminosity $L_{\rm max}$ is
%%%
\begin{eqnarray}
\mathcal{P}(L_{\rm max}) &\cdot & dL_{\rm max} \\
&=& N \cdot p (L_{\rm max}) \cdot P^{N-1}(<L_{\rm max}) \cdot dL_{\rm max} \\
&=& N C L_{\rm max}^{-\alpha } \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1}
\end{eqnarray}
%%%
Thus, the expected value for the maximum luminosity is
%%%
\begin{eqnarray}
\langle L_{\rm max} \rangle (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
&=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1} \\
&\equiv & N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max})
\end{eqnarray}
%%%
